Abstract Plots

### 2021-08-19 Abstract.Rmd
small changes to generate markdown

summary(model2)

@@

```{r}
ggplot(data = sens.spec.data.2, aes(x = cosine_similarity, y = value, color = measure))+
  geom_point()+
  geom_smooth(method = lm, se = FALSE)+
  labs(title = "Sensitivity & Specificity vs. Cosine Similarity to FFPE Signature", x = "Cosine Similarity of COSMIC Signature to FFPE", y = "Average Sensitivity and Specificity (10 iterations)")
```

>>>>

model2_summary <- summary(model2)

@@
